Evolution of the AGN UV luminosity function from redshift 7.5

### 2019-02-25 Paper/paper.tex
Update

We thank Eilat Glikman, Linhua Jiang, Nobunari Kashi\-kawa, Ian
McGreer, Nick Ross, Chris Willott, and Jinyi Yang for sharing data and
especially for sharing their quasar selection functions.  It is a
pleasure to acknowledge useful discussions with James Aird, Eduardo
Ba\~nados, Manda Banerji, Tirthankar Roy Choudhury, George Efstathiou,
Xiaohui Fan, Andrea Ferrara, Prakash Gaikwad, Francesco Haardt, Martin
Haehnelt, Paul Hewett, David Hogg, Vikram Khaire, Sergey Koposov,
Donald Lynden-Bell, Roberto Maiolino, Richard McMahon, Daniel
Mortlock, Ewald Puchwein, Gordon Richards, Alberto Rorai, Bram
Venemans and Stephen Warren.  \new{We thank the anonymous referee for
  their comments.} GK acknowledges support from ERC Advanced Grant
320596 `The Emergence of Structure During the Epoch of Reionization'.

@@

    0.0 & 23.20^{+0.20}_{-0.18} & 22.96^{+0.11}_{-0.14} & 23.08^{+0.20}_{-0.18} & 22.84^{+0.11}_{-0.14} & -13.71^{+0.05}_{-0.05} & -13.86^{+0.03}_{-0.03} \\
    0.1 & 23.43^{+0.15}_{-0.14} & 23.19^{+0.09}_{-0.11} & 23.30^{+0.15}_{-0.14} & 23.07^{+0.09}_{-0.11} & -13.51^{+0.04}_{-0.04} & -13.66^{+0.02}_{-0.03} \\
    0.2 & 23.62^{+0.11}_{-0.11} & 23.39^{+0.07}_{-0.08} & 23.50^{+0.11}_{-0.11} & 23.27^{+0.07}_{-0.08} & -13.33^{+0.04}_{-0.04} & -13.48^{+0.02}_{-0.02} \\
    0.3 & 23.80^{+0.07}_{-0.09} & 23.58^{+0.05}_{-0.06} & 23.68^{+0.07}_{-0.09} & 23.46^{+0.05}_{-0.06} & -13.17^{+0.03}_{-0.03} & -13.31^{+0.02}_{-0.02} \\
    0.4 & 23.96^{+0.06}_{-0.07} & 23.75^{+0.04}_{-0.04} & 23.83^{+0.06}_{-0.07} & 23.63^{+0.04}_{-0.04} & -13.02^{+0.03}_{-0.03} & -13.16^{+0.02}_{-0.02} \\
    0.5 & 24.10^{+0.04}_{-0.06} & 23.91^{+0.03}_{-0.03} & 23.97^{+0.04}_{-0.06} & 23.78^{+0.03}_{-0.03} & -12.89^{+0.02}_{-0.02} & -13.02^{+0.01}_{-0.01} \\
    0.6 & 24.23^{+0.03}_{-0.04} & 24.05^{+0.02}_{-0.02} & 24.10^{+0.03}_{-0.04} & 23.93^{+0.02}_{-0.02} & -12.77^{+0.02}_{-0.02} & -12.89^{+0.01}_{-0.01} \\
    0.7 & 24.34^{+0.02}_{-0.03} & 24.18^{+0.01}_{-0.01} & 24.22^{+0.02}_{-0.03} & 24.06^{+0.01}_{-0.01} & -12.66^{+0.02}_{-0.02} & -12.78^{+0.01}_{-0.01} \\
    0.8 & 24.45^{+0.02}_{-0.02} & 24.30^{+0.01}_{-0.01} & 24.33^{+0.02}_{-0.02} & 24.18^{+0.01}_{-0.01} & -12.56^{+0.02}_{-0.02} & -12.67^{+0.01}_{-0.01} \\
    0.9 & 24.55^{+0.01}_{-0.02} & 24.41^{+0.01}_{-0.01} & 24.42^{+0.01}_{-0.02} & 24.29^{+0.01}_{-0.01} & -12.47^{+0.02}_{-0.02} & -12.58^{+0.01}_{-0.01} \\
    1.0 & 24.63^{+0.01}_{-0.02} & 24.51^{+0.01}_{-0.01} & 24.51^{+0.01}_{-0.02} & 24.39^{+0.01}_{-0.01} & -12.39^{+0.02}_{-0.02} & -12.49^{+0.01}_{-0.01} \\
    1.1 & 24.71^{+0.01}_{-0.01} & 24.60^{+0.01}_{-0.01} & 24.59^{+0.01}_{-0.01} & 24.48^{+0.01}_{-0.01} & -12.32^{+0.02}_{-0.02} & -12.42^{+0.01}_{-0.01} \\
    1.2 & 24.78^{+0.01}_{-0.01} & 24.68^{+0.01}_{-0.01} & 24.66^{+0.01}_{-0.01} & 24.56^{+0.01}_{-0.01} & -12.26^{+0.02}_{-0.02} & -12.35^{+0.01}_{-0.01} \\
    1.3 & 24.84^{+0.01}_{-0.01} & 24.75^{+0.01}_{-0.01} & 24.72^{+0.01}_{-0.01} & 24.63^{+0.01}_{-0.01} & -12.21^{+0.02}_{-0.02} & -12.30^{+0.01}_{-0.01} \\
    1.4 & 24.90^{+0.01}_{-0.01} & 24.81^{+0.01}_{-0.01} & 24.78^{+0.01}_{-0.01} & 24.69^{+0.01}_{-0.01} & -12.16^{+0.02}_{-0.02} & -12.25^{+0.01}_{-0.01} \\
    1.5 & 24.95^{+0.01}_{-0.01} & 24.87^{+0.01}_{-0.01} & 24.83^{+0.01}_{-0.01} & 24.75^{+0.01}_{-0.01} & -12.12^{+0.02}_{-0.02} & -12.21^{+0.01}_{-0.01} \\
    1.6 & 24.99^{+0.01}_{-0.01} & 24.91^{+0.01}_{-0.01} & 24.87^{+0.01}_{-0.01} & 24.79^{+0.01}_{-0.01} & -12.09^{+0.02}_{-0.02} & -12.18^{+0.01}_{-0.01} \\
    1.7 & 25.03^{+0.01}_{-0.01} & 24.95^{+0.01}_{-0.01} & 24.91^{+0.01}_{-0.01} & 24.83^{+0.01}_{-0.01} & -12.07^{+0.03}_{-0.03} & -12.16^{+0.02}_{-0.02} \\
    1.8 & 25.06^{+0.01}_{-0.01} & 24.98^{+0.01}_{-0.01} & 24.94^{+0.01}_{-0.01} & 24.86^{+0.01}_{-0.01} & -12.05^{+0.03}_{-0.03} & -12.15^{+0.02}_{-0.02} \\
    1.9 & 25.09^{+0.02}_{-0.02} & 25.01^{+0.01}_{-0.01} & 24.97^{+0.02}_{-0.02} & 24.88^{+0.01}_{-0.01} & -12.04^{+0.03}_{-0.04} & -12.14^{+0.02}_{-0.02} \\
    2.0 & 25.11^{+0.02}_{-0.02} & 25.02^{+0.01}_{-0.01} & 24.99^{+0.02}_{-0.02} & 24.90^{+0.01}_{-0.01} & -12.03^{+0.04}_{-0.04} & -12.14^{+0.02}_{-0.02} \\
    2.1 & 25.12^{+0.03}_{-0.03} & 25.03^{+0.02}_{-0.02} & 25.00^{+0.03}_{-0.03} & 24.91^{+0.02}_{-0.02} & -12.02^{+0.04}_{-0.05} & -12.14^{+0.03}_{-0.03} \\
    2.2 & 25.14^{+0.03}_{-0.03} & 25.04^{+0.02}_{-0.02} & 25.01^{+0.03}_{-0.03} & 24.91^{+0.02}_{-0.02} & -12.03^{+0.05}_{-0.05} & -12.15^{+0.03}_{-0.03} \\
    2.3 & 25.14^{+0.03}_{-0.04} & 25.04^{+0.02}_{-0.02} & 25.02^{+0.03}_{-0.04} & 24.91^{+0.02}_{-0.02} & -12.03^{+0.05}_{-0.06} & -12.16^{+0.03}_{-0.03} \\
    2.4 & 25.14^{+0.04}_{-0.05} & 25.03^{+0.03}_{-0.03} & 25.02^{+0.04}_{-0.05} & 24.91^{+0.03}_{-0.03} & -12.04^{+0.05}_{-0.07} & -12.18^{+0.04}_{-0.04} \\
    2.5 & 25.14^{+0.04}_{-0.06} & 25.02^{+0.03}_{-0.03} & 25.02^{+0.04}_{-0.06} & 24.89^{+0.03}_{-0.03} & -12.05^{+0.06}_{-0.07} & -12.20^{+0.04}_{-0.04} \\
    2.6 & 25.14^{+0.05}_{-0.06} & 25.00^{+0.04}_{-0.04} & 25.01^{+0.05}_{-0.06} & 24.88^{+0.04}_{-0.04} & -12.07^{+0.07}_{-0.08} & -12.23^{+0.04}_{-0.04} \\
    2.7 & 25.13^{+0.06}_{-0.07} & 24.98^{+0.04}_{-0.04} & 25.00^{+0.06}_{-0.07} & 24.86^{+0.04}_{-0.04} & -12.09^{+0.07}_{-0.09} & -12.25^{+0.05}_{-0.05} \\
    2.8 & 25.11^{+0.07}_{-0.07} & 24.96^{+0.04}_{-0.05} & 24.99^{+0.07}_{-0.07} & 24.84^{+0.04}_{-0.05} & -12.11^{+0.08}_{-0.09} & -12.29^{+0.05}_{-0.05} \\
    2.9 & 25.10^{+0.07}_{-0.08} & 24.93^{+0.05}_{-0.05} & 24.98^{+0.07}_{-0.08} & 24.81^{+0.05}_{-0.05} & -12.14^{+0.08}_{-0.10} & -12.32^{+0.05}_{-0.05} \\
    3.0 & 25.08^{+0.08}_{-0.09} & 24.91^{+0.05}_{-0.05} & 24.96^{+0.08}_{-0.09} & 24.78^{+0.05}_{-0.05} & -12.16^{+0.09}_{-0.11} & -12.36^{+0.05}_{-0.06} \\
    3.1 & 25.06^{+0.08}_{-0.10} & 24.87^{+0.05}_{-0.05} & 24.94^{+0.08}_{-0.10} & 24.75^{+0.05}_{-0.05} & -12.20^{+0.09}_{-0.12} & -12.40^{+0.06}_{-0.06} \\
    3.2 & 25.04^{+0.09}_{-0.11} & 24.84^{+0.06}_{-0.05} & 24.92^{+0.09}_{-0.11} & 24.72^{+0.06}_{-0.05} & -12.23^{+0.10}_{-0.13} & -12.44^{+0.06}_{-0.06} \\
    3.3 & 25.01^{+0.09}_{-0.12} & 24.81^{+0.06}_{-0.06} & 24.89^{+0.09}_{-0.12} & 24.68^{+0.06}_{-0.06} & -12.27^{+0.10}_{-0.13} & -12.49^{+0.06}_{-0.06} \\
    3.4 & 24.99^{+0.10}_{-0.13} & 24.77^{+0.06}_{-0.06} & 24.86^{+0.10}_{-0.13} & 24.64^{+0.06}_{-0.06} & -12.30^{+0.11}_{-0.14} & -12.54^{+0.06}_{-0.07} \\
    3.5 & 24.96^{+0.10}_{-0.14} & 24.73^{+0.06}_{-0.06} & 24.83^{+0.10}_{-0.14} & 24.60^{+0.06}_{-0.06} & -12.34^{+0.11}_{-0.15} & -12.59^{+0.06}_{-0.07} \\
    3.6 & 24.93^{+0.11}_{-0.15} & 24.69^{+0.06}_{-0.07} & 24.80^{+0.11}_{-0.15} & 24.56^{+0.06}_{-0.07} & -12.39^{+0.11}_{-0.16} & -12.64^{+0.06}_{-0.07} \\
    3.7 & 24.89^{+0.11}_{-0.15} & 24.64^{+0.06}_{-0.07} & 24.77^{+0.11}_{-0.15} & 24.52^{+0.06}_{-0.07} & -12.43^{+0.12}_{-0.16} & -12.69^{+0.06}_{-0.07} \\
    3.8 & 24.85^{+0.12}_{-0.16} & 24.60^{+0.06}_{-0.07} & 24.73^{+0.12}_{-0.16} & 24.47^{+0.06}_{-0.07} & -12.48^{+0.12}_{-0.17} & -12.74^{+0.07}_{-0.08} \\
    3.9 & 24.81^{+0.12}_{-0.17} & 24.55^{+0.07}_{-0.07} & 24.69^{+0.12}_{-0.17} & 24.43^{+0.07}_{-0.07} & -12.53^{+0.13}_{-0.18} & -12.80^{+0.07}_{-0.08} \\
    4.0 & 24.78^{+0.13}_{-0.18} & 24.51^{+0.07}_{-0.08} & 24.65^{+0.13}_{-0.18} & 24.38^{+0.07}_{-0.08} & -12.57^{+0.13}_{-0.19} & -12.85^{+0.07}_{-0.09} \\
    4.1 & 24.74^{+0.13}_{-0.19} & 24.46^{+0.07}_{-0.09} & 24.61^{+0.13}_{-0.19} & 24.34^{+0.07}_{-0.09} & -12.63^{+0.14}_{-0.20} & -12.91^{+0.07}_{-0.10} \\
    4.2 & 24.69^{+0.13}_{-0.19} & 24.41^{+0.07}_{-0.09} & 24.57^{+0.13}_{-0.19} & 24.29^{+0.07}_{-0.09} & -12.68^{+0.14}_{-0.21} & -12.97^{+0.07}_{-0.10} \\
    4.3 & 24.65^{+0.14}_{-0.20} & 24.36^{+0.07}_{-0.10} & 24.53^{+0.14}_{-0.20} & 24.24^{+0.07}_{-0.10} & -12.73^{+0.15}_{-0.22} & -13.03^{+0.07}_{-0.11} \\
    4.4 & 24.61^{+0.14}_{-0.21} & 24.31^{+0.07}_{-0.11} & 24.49^{+0.14}_{-0.21} & 24.19^{+0.07}_{-0.11} & -12.78^{+0.15}_{-0.23} & -13.09^{+0.08}_{-0.12} \\
    4.5 & 24.57^{+0.15}_{-0.23} & 24.26^{+0.08}_{-0.11} & 24.44^{+0.15}_{-0.23} & 24.14^{+0.08}_{-0.11} & -12.84^{+0.16}_{-0.24} & -13.15^{+0.08}_{-0.12} \\
    4.6 & 24.52^{+0.16}_{-0.24} & 24.21^{+0.08}_{-0.12} & 24.39^{+0.16}_{-0.24} & 24.08^{+0.08}_{-0.12} & -12.90^{+0.17}_{-0.25} & -13.22^{+0.08}_{-0.13} \\
    4.7 & 24.47^{+0.17}_{-0.25} & 24.15^{+0.08}_{-0.13} & 24.34^{+0.17}_{-0.25} & 24.03^{+0.08}_{-0.13} & -12.96^{+0.18}_{-0.27} & -13.28^{+0.08}_{-0.14} \\
    4.8 & 24.42^{+0.17}_{-0.27} & 24.10^{+0.08}_{-0.13} & 24.30^{+0.17}_{-0.27} & 23.98^{+0.08}_{-0.13} & -13.02^{+0.18}_{-0.28} & -13.35^{+0.08}_{-0.14} \\
    4.9 & 24.37^{+0.18}_{-0.28} & 24.04^{+0.08}_{-0.14} & 24.25^{+0.18}_{-0.28} & 23.92^{+0.08}_{-0.14} & -13.08^{+0.19}_{-0.29} & -13.41^{+0.09}_{-0.15} \\
    5.0 & 24.31^{+0.20}_{-0.29} & 23.99^{+0.08}_{-0.15} & 24.19^{+0.20}_{-0.29} & 23.87^{+0.08}_{-0.15} & -13.15^{+0.20}_{-0.30} & -13.48^{+0.09}_{-0.16} \\

@@

    5.1 & 24.27^{+0.20}_{-0.30} & 23.93^{+0.09}_{-0.15} & 24.14^{+0.20}_{-0.30} & 23.81^{+0.09}_{-0.15} & -13.21^{+0.21}_{-0.32} & -13.55^{+0.09}_{-0.16} \\
    5.2 & 24.22^{+0.21}_{-0.32} & 23.88^{+0.09}_{-0.17} & 24.09^{+0.21}_{-0.32} & 23.75^{+0.09}_{-0.17} & -13.27^{+0.22}_{-0.33} & -13.62^{+0.10}_{-0.17} \\
    5.3 & 24.16^{+0.22}_{-0.33} & 23.82^{+0.10}_{-0.18} & 24.03^{+0.22}_{-0.33} & 23.69^{+0.10}_{-0.18} & -13.34^{+0.23}_{-0.34} & -13.69^{+0.11}_{-0.18} \\
    5.4 & 24.10^{+0.24}_{-0.34} & 23.75^{+0.11}_{-0.19} & 23.98^{+0.24}_{-0.34} & 23.63^{+0.11}_{-0.19} & -13.42^{+0.24}_{-0.36} & -13.77^{+0.11}_{-0.19} \\
    5.5 & 24.05^{+0.24}_{-0.36} & 23.69^{+0.12}_{-0.19} & 23.93^{+0.24}_{-0.36} & 23.57^{+0.12}_{-0.19} & -13.49^{+0.25}_{-0.37} & -13.85^{+0.12}_{-0.20} \\
    5.6 & 23.99^{+0.26}_{-0.38} & 23.63^{+0.12}_{-0.20} & 23.87^{+0.26}_{-0.38} & 23.50^{+0.12}_{-0.20} & -13.59^{+0.27}_{-0.38} & -13.95^{+0.12}_{-0.21} \\
    5.7 & 23.93^{+0.27}_{-0.38} & 23.57^{+0.12}_{-0.22} & 23.81^{+0.27}_{-0.38} & 23.45^{+0.12}_{-0.22} & -13.69^{+0.28}_{-0.39} & -14.05^{+0.13}_{-0.22} \\

>>>>

We thank Eilat Glikman, Linhua Jiang, Nobunari Kashi\-kawa, Ian
McGreer, Nick Ross, Chris Willott, and Jinyi Yang for sharing data and
especially for sharing their quasar selection functions.  It is a
pleasure to acknowledge useful discussions with James Aird, Eduardo
Ba\~nados, Manda Banerji, Tirthankar Roy Choudhury, George Efstathiou,
Xiaohui Fan, Andrea Ferrara, Prakash Gaikwad, Francesco Haardt, Martin
Haehnelt, Paul Hewett, David Hogg, Vikram Khaire, Sergey Koposov, Alex
Krolewski, Donald Lynden-Bell, Roberto Maiolino, Richard McMahon,
Daniel Mortlock, Ewald Puchwein, Gordon Richards, Alberto Rorai, Bram
Venemans and Stephen Warren.  \new{We thank the anonymous referee for
  their comments.} GK acknowledges support from ERC Advanced Grant
320596 `The Emergence of Structure During the Epoch of Reionization'.

@@

    0.0 & 23.13^{+0.33}_{-0.20} & 22.79^{+0.13}_{-0.15} & 23.01^{+0.33}_{-0.20} & 22.67^{+0.13}_{-0.15} & -13.66^{+0.08}_{-0.05} & -13.86^{+0.03}_{-0.03} \\
    0.1 & 23.39^{+0.25}_{-0.16} & 23.06^{+0.10}_{-0.12} & 23.27^{+0.25}_{-0.16} & 22.94^{+0.10}_{-0.12} & -13.45^{+0.06}_{-0.05} & -13.65^{+0.03}_{-0.02} \\
    0.2 & 23.61^{+0.18}_{-0.13} & 23.30^{+0.08}_{-0.09} & 23.49^{+0.18}_{-0.13} & 23.18^{+0.08}_{-0.09} & -13.27^{+0.05}_{-0.04} & -13.46^{+0.02}_{-0.02} \\
    0.3 & 23.81^{+0.13}_{-0.11} & 23.52^{+0.06}_{-0.06} & 23.69^{+0.13}_{-0.11} & 23.39^{+0.06}_{-0.06} & -13.10^{+0.04}_{-0.04} & -13.29^{+0.02}_{-0.02} \\
    0.4 & 23.99^{+0.09}_{-0.09} & 23.71^{+0.04}_{-0.04} & 23.86^{+0.09}_{-0.09} & 23.59^{+0.04}_{-0.04} & -12.95^{+0.04}_{-0.03} & -13.13^{+0.02}_{-0.02} \\
    0.5 & 24.14^{+0.07}_{-0.07} & 23.89^{+0.03}_{-0.03} & 24.02^{+0.07}_{-0.07} & 23.76^{+0.03}_{-0.03} & -12.82^{+0.03}_{-0.03} & -12.98^{+0.01}_{-0.01} \\
    0.6 & 24.28^{+0.05}_{-0.05} & 24.05^{+0.02}_{-0.02} & 24.16^{+0.05}_{-0.05} & 23.92^{+0.02}_{-0.02} & -12.69^{+0.03}_{-0.03} & -12.85^{+0.01}_{-0.01} \\
    0.7 & 24.41^{+0.04}_{-0.03} & 24.19^{+0.02}_{-0.02} & 24.28^{+0.04}_{-0.03} & 24.07^{+0.02}_{-0.02} & -12.58^{+0.02}_{-0.02} & -12.74^{+0.01}_{-0.01} \\
    0.8 & 24.52^{+0.03}_{-0.03} & 24.32^{+0.01}_{-0.01} & 24.40^{+0.03}_{-0.03} & 24.20^{+0.01}_{-0.01} & -12.48^{+0.02}_{-0.02} & -12.63^{+0.01}_{-0.01} \\
    0.9 & 24.62^{+0.02}_{-0.02} & 24.44^{+0.01}_{-0.01} & 24.50^{+0.02}_{-0.02} & 24.31^{+0.01}_{-0.01} & -12.39^{+0.02}_{-0.02} & -12.53^{+0.01}_{-0.01} \\
    1.0 & 24.71^{+0.02}_{-0.02} & 24.54^{+0.01}_{-0.01} & 24.59^{+0.02}_{-0.02} & 24.42^{+0.01}_{-0.01} & -12.31^{+0.02}_{-0.02} & -12.44^{+0.01}_{-0.01} \\
    1.1 & 24.79^{+0.02}_{-0.02} & 24.64^{+0.01}_{-0.01} & 24.67^{+0.02}_{-0.02} & 24.52^{+0.01}_{-0.01} & -12.24^{+0.02}_{-0.02} & -12.37^{+0.01}_{-0.01} \\
    1.2 & 24.87^{+0.02}_{-0.02} & 24.72^{+0.01}_{-0.01} & 24.75^{+0.02}_{-0.02} & 24.60^{+0.01}_{-0.01} & -12.17^{+0.02}_{-0.02} & -12.30^{+0.01}_{-0.01} \\
    1.3 & 24.93^{+0.02}_{-0.02} & 24.80^{+0.01}_{-0.01} & 24.81^{+0.02}_{-0.02} & 24.68^{+0.01}_{-0.01} & -12.12^{+0.02}_{-0.02} & -12.24^{+0.01}_{-0.01} \\
    1.4 & 24.99^{+0.02}_{-0.02} & 24.86^{+0.01}_{-0.01} & 24.87^{+0.02}_{-0.02} & 24.74^{+0.01}_{-0.01} & -12.08^{+0.02}_{-0.03} & -12.19^{+0.01}_{-0.01} \\
    1.5 & 25.04^{+0.02}_{-0.02} & 24.92^{+0.01}_{-0.01} & 24.92^{+0.02}_{-0.02} & 24.80^{+0.01}_{-0.01} & -12.04^{+0.02}_{-0.03} & -12.15^{+0.02}_{-0.01} \\
    1.6 & 25.08^{+0.02}_{-0.02} & 24.97^{+0.01}_{-0.01} & 24.96^{+0.02}_{-0.02} & 24.85^{+0.01}_{-0.01} & -12.01^{+0.03}_{-0.03} & -12.12^{+0.02}_{-0.02} \\
    1.7 & 25.12^{+0.02}_{-0.02} & 25.01^{+0.01}_{-0.01} & 25.00^{+0.02}_{-0.02} & 24.89^{+0.01}_{-0.01} & -11.99^{+0.03}_{-0.03} & -12.10^{+0.02}_{-0.02} \\
    1.8 & 25.15^{+0.02}_{-0.02} & 25.04^{+0.01}_{-0.01} & 25.03^{+0.02}_{-0.02} & 24.92^{+0.01}_{-0.01} & -11.97^{+0.03}_{-0.04} & -12.08^{+0.02}_{-0.02} \\
    1.9 & 25.17^{+0.02}_{-0.02} & 25.07^{+0.01}_{-0.01} & 25.05^{+0.02}_{-0.02} & 24.94^{+0.01}_{-0.01} & -11.96^{+0.04}_{-0.04} & -12.07^{+0.02}_{-0.02} \\
    2.0 & 25.19^{+0.03}_{-0.03} & 25.08^{+0.01}_{-0.01} & 25.07^{+0.03}_{-0.03} & 24.96^{+0.01}_{-0.01} & -11.95^{+0.04}_{-0.05} & -12.07^{+0.03}_{-0.03} \\
    2.1 & 25.20^{+0.03}_{-0.04} & 25.10^{+0.02}_{-0.02} & 25.08^{+0.03}_{-0.04} & 24.97^{+0.02}_{-0.02} & -11.95^{+0.04}_{-0.05} & -12.07^{+0.03}_{-0.03} \\
    2.2 & 25.21^{+0.03}_{-0.05} & 25.10^{+0.02}_{-0.02} & 25.09^{+0.03}_{-0.05} & 24.98^{+0.02}_{-0.02} & -11.95^{+0.05}_{-0.06} & -12.08^{+0.03}_{-0.03} \\
    2.3 & 25.22^{+0.04}_{-0.05} & 25.10^{+0.03}_{-0.03} & 25.09^{+0.04}_{-0.05} & 24.98^{+0.03}_{-0.03} & -11.96^{+0.05}_{-0.07} & -12.09^{+0.04}_{-0.04} \\
    2.4 & 25.22^{+0.05}_{-0.06} & 25.10^{+0.03}_{-0.03} & 25.09^{+0.05}_{-0.06} & 24.97^{+0.03}_{-0.03} & -11.97^{+0.06}_{-0.07} & -12.11^{+0.04}_{-0.04} \\
    2.5 & 25.21^{+0.05}_{-0.06} & 25.09^{+0.04}_{-0.04} & 25.09^{+0.05}_{-0.06} & 24.97^{+0.04}_{-0.04} & -11.99^{+0.06}_{-0.08} & -12.13^{+0.05}_{-0.04} \\
    2.6 & 25.21^{+0.05}_{-0.07} & 25.07^{+0.04}_{-0.04} & 25.08^{+0.05}_{-0.07} & 24.95^{+0.04}_{-0.04} & -12.01^{+0.07}_{-0.08} & -12.15^{+0.05}_{-0.04} \\
    2.7 & 25.19^{+0.06}_{-0.07} & 25.05^{+0.05}_{-0.04} & 25.07^{+0.06}_{-0.07} & 24.93^{+0.05}_{-0.04} & -12.03^{+0.07}_{-0.09} & -12.18^{+0.05}_{-0.05} \\
    2.8 & 25.18^{+0.07}_{-0.08} & 25.03^{+0.05}_{-0.05} & 25.06^{+0.06}_{-0.08} & 24.91^{+0.05}_{-0.05} & -12.05^{+0.08}_{-0.09} & -12.22^{+0.06}_{-0.05} \\
    2.9 & 25.16^{+0.07}_{-0.09} & 25.01^{+0.05}_{-0.05} & 25.04^{+0.07}_{-0.09} & 24.89^{+0.05}_{-0.05} & -12.08^{+0.08}_{-0.10} & -12.25^{+0.06}_{-0.05} \\
    3.0 & 25.14^{+0.08}_{-0.09} & 24.98^{+0.06}_{-0.05} & 25.02^{+0.08}_{-0.09} & 24.86^{+0.06}_{-0.05} & -12.11^{+0.09}_{-0.10} & -12.29^{+0.06}_{-0.05} \\
    3.1 & 25.12^{+0.08}_{-0.10} & 24.95^{+0.06}_{-0.05} & 25.00^{+0.08}_{-0.10} & 24.83^{+0.06}_{-0.05} & -12.14^{+0.09}_{-0.11} & -12.33^{+0.06}_{-0.05} \\
    3.2 & 25.09^{+0.09}_{-0.11} & 24.91^{+0.06}_{-0.05} & 24.97^{+0.09}_{-0.11} & 24.79^{+0.06}_{-0.05} & -12.18^{+0.10}_{-0.12} & -12.37^{+0.07}_{-0.06} \\
    3.3 & 25.06^{+0.09}_{-0.11} & 24.88^{+0.06}_{-0.06} & 24.94^{+0.09}_{-0.11} & 24.75^{+0.06}_{-0.06} & -12.22^{+0.10}_{-0.12} & -12.42^{+0.07}_{-0.06} \\
    3.4 & 25.03^{+0.10}_{-0.11} & 24.84^{+0.07}_{-0.05} & 24.91^{+0.10}_{-0.11} & 24.71^{+0.07}_{-0.05} & -12.26^{+0.11}_{-0.13} & -12.47^{+0.07}_{-0.06} \\
    3.5 & 25.00^{+0.10}_{-0.12} & 24.80^{+0.07}_{-0.06} & 24.88^{+0.10}_{-0.12} & 24.68^{+0.07}_{-0.06} & -12.30^{+0.11}_{-0.13} & -12.52^{+0.07}_{-0.07} \\
    3.6 & 24.97^{+0.11}_{-0.12} & 24.76^{+0.07}_{-0.07} & 24.84^{+0.11}_{-0.12} & 24.63^{+0.07}_{-0.07} & -12.34^{+0.11}_{-0.14} & -12.57^{+0.07}_{-0.07} \\
    3.7 & 24.93^{+0.11}_{-0.13} & 24.71^{+0.07}_{-0.07} & 24.81^{+0.11}_{-0.13} & 24.59^{+0.07}_{-0.07} & -12.38^{+0.11}_{-0.15} & -12.63^{+0.07}_{-0.08} \\
    3.8 & 24.90^{+0.11}_{-0.15} & 24.66^{+0.07}_{-0.07} & 24.78^{+0.11}_{-0.15} & 24.54^{+0.07}_{-0.07} & -12.43^{+0.12}_{-0.16} & -12.68^{+0.07}_{-0.08} \\
    3.9 & 24.86^{+0.11}_{-0.16} & 24.61^{+0.07}_{-0.08} & 24.74^{+0.11}_{-0.16} & 24.49^{+0.07}_{-0.08} & -12.48^{+0.12}_{-0.17} & -12.74^{+0.07}_{-0.08} \\
    4.0 & 24.83^{+0.11}_{-0.18} & 24.57^{+0.07}_{-0.08} & 24.71^{+0.11}_{-0.18} & 24.44^{+0.07}_{-0.08} & -12.52^{+0.12}_{-0.19} & -12.80^{+0.07}_{-0.09} \\
    4.1 & 24.79^{+0.12}_{-0.19} & 24.51^{+0.07}_{-0.09} & 24.67^{+0.12}_{-0.19} & 24.39^{+0.07}_{-0.09} & -12.58^{+0.13}_{-0.19} & -12.87^{+0.07}_{-0.09} \\
    4.2 & 24.74^{+0.13}_{-0.19} & 24.46^{+0.07}_{-0.09} & 24.62^{+0.13}_{-0.19} & 24.34^{+0.07}_{-0.09} & -12.63^{+0.14}_{-0.20} & -12.93^{+0.07}_{-0.09} \\
    4.3 & 24.70^{+0.14}_{-0.20} & 24.40^{+0.07}_{-0.09} & 24.57^{+0.14}_{-0.20} & 24.28^{+0.07}_{-0.09} & -12.69^{+0.15}_{-0.21} & -12.99^{+0.08}_{-0.10} \\
    4.4 & 24.65^{+0.15}_{-0.21} & 24.35^{+0.08}_{-0.10} & 24.53^{+0.15}_{-0.21} & 24.22^{+0.08}_{-0.10} & -12.75^{+0.15}_{-0.22} & -13.06^{+0.08}_{-0.11} \\
    4.5 & 24.60^{+0.15}_{-0.22} & 24.29^{+0.08}_{-0.10} & 24.48^{+0.15}_{-0.22} & 24.17^{+0.08}_{-0.10} & -12.80^{+0.16}_{-0.23} & -13.13^{+0.08}_{-0.12} \\
    4.6 & 24.56^{+0.15}_{-0.22} & 24.24^{+0.08}_{-0.12} & 24.43^{+0.15}_{-0.22} & 24.11^{+0.08}_{-0.12} & -12.86^{+0.16}_{-0.24} & -13.20^{+0.08}_{-0.13} \\
    4.7 & 24.51^{+0.16}_{-0.23} & 24.17^{+0.09}_{-0.13} & 24.39^{+0.16}_{-0.23} & 24.05^{+0.09}_{-0.13} & -12.92^{+0.17}_{-0.25} & -13.27^{+0.09}_{-0.14} \\
    4.8 & 24.46^{+0.17}_{-0.25} & 24.11^{+0.09}_{-0.14} & 24.34^{+0.17}_{-0.25} & 23.99^{+0.09}_{-0.14} & -12.98^{+0.17}_{-0.26} & -13.34^{+0.09}_{-0.15} \\
    4.9 & 24.41^{+0.18}_{-0.26} & 24.05^{+0.09}_{-0.15} & 24.29^{+0.18}_{-0.26} & 23.93^{+0.09}_{-0.15} & -13.04^{+0.18}_{-0.27} & -13.41^{+0.09}_{-0.16} \\
    5.0 & 24.36^{+0.17}_{-0.28} & 23.99^{+0.09}_{-0.16} & 24.24^{+0.17}_{-0.28} & 23.87^{+0.09}_{-0.16} & -13.10^{+0.18}_{-0.29} & -13.49^{+0.09}_{-0.17} \\

@@

    5.1 & 24.31^{+0.18}_{-0.29} & 23.93^{+0.09}_{-0.17} & 24.18^{+0.18}_{-0.29} & 23.80^{+0.09}_{-0.17} & -13.17^{+0.19}_{-0.30} & -13.56^{+0.10}_{-0.17} \\
    5.2 & 24.25^{+0.19}_{-0.30} & 23.86^{+0.10}_{-0.17} & 24.13^{+0.19}_{-0.30} & 23.74^{+0.10}_{-0.17} & -13.24^{+0.20}_{-0.31} & -13.64^{+0.11}_{-0.18} \\
    5.3 & 24.19^{+0.20}_{-0.32} & 23.79^{+0.11}_{-0.19} & 24.07^{+0.20}_{-0.32} & 23.67^{+0.11}_{-0.19} & -13.31^{+0.21}_{-0.33} & -13.72^{+0.12}_{-0.20} \\
    5.4 & 24.14^{+0.22}_{-0.33} & 23.73^{+0.12}_{-0.20} & 24.01^{+0.22}_{-0.33} & 23.60^{+0.12}_{-0.20} & -13.38^{+0.23}_{-0.34} & -13.80^{+0.13}_{-0.21} \\
    5.5 & 24.08^{+0.23}_{-0.34} & 23.66^{+0.13}_{-0.21} & 23.95^{+0.23}_{-0.34} & 23.53^{+0.13}_{-0.21} & -13.47^{+0.24}_{-0.36} & -13.89^{+0.14}_{-0.22} \\
    5.6 & 24.01^{+0.24}_{-0.36} & 23.59^{+0.14}_{-0.23} & 23.89^{+0.24}_{-0.36} & 23.47^{+0.14}_{-0.23} & -13.56^{+0.25}_{-0.37} & -14.00^{+0.14}_{-0.24} \\
    5.7 & 23.96^{+0.25}_{-0.38} & 23.52^{+0.15}_{-0.25} & 23.84^{+0.25}_{-0.38} & 23.40^{+0.15}_{-0.25} & -13.66^{+0.26}_{-0.39} & -14.11^{+0.15}_{-0.25} \\
